\documentclass[12pt]{scrartcl}
%\printanswers


\setlength{\parindent}{0pt}
\setlength{\parskip}{.25cm}

\usepackage{graphicx}

\usepackage{xcolor}

\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\usepackage{hyperref}
\hypersetup{
  letterpaper,
  colorlinks,
  linkcolor=red,
  citecolor=darkgreen,
  menucolor=darkred,
  urlcolor=blue,
  pdfpagemode=none,
  pdftitle={CS2 - Lab Worksheet},
  pdfauthor={~},
  pdfsubject={},
  pdfkeywords={}
}

\definecolor{MyDarkBlue}{rgb}{0,0.08,0.45}
\definecolor{MyDarkRed}{rgb}{0.45,0.08,0}
\definecolor{MyDarkGreen}{rgb}{0.08,0.45,0.08}

\definecolor{mintedBackground}{rgb}{0.95,0.95,0.95}
\definecolor{mintedInlineBackground}{rgb}{.90,.90,1}

%\usepackage{newfloat}
\usepackage[newfloat=true]{minted}
\setminted{mathescape,
               linenos,
               autogobble,
               frame=none,
               framesep=2mm,
               framerule=0.4pt,
               %label=foo,
               xleftmargin=2em,
               xrightmargin=0em,
               startinline=true,  %PHP only, allow it to omit the PHP Tags *** with this option, variables using dollar sign in comments are treated as latex math
               numbersep=10pt, %gap between line numbers and start of line
               style=default, %syntax highlighting style, default is "default"
               			    %gallery: http://help.farbox.com/pygments.html
			    	    %list available: pygmentize -L styles
               bgcolor=mintedBackground} %prevents breaking across pages
               
\setmintedinline{bgcolor={mintedBackground}}
\setminted[text]{bgcolor={mintedBackground},linenos=false,autogobble,xleftmargin=1em}
%\setminted[php]{bgcolor=mintedBackgroundPHP} %startinline=True}
\SetupFloatingEnvironment{listing}{name=Code Sample}
\SetupFloatingEnvironment{listing}{listname=List of Code Samples}


\begin{document}

\section*{CSCE 156 - Lab 9.0 - JDBC in a Web App I - Worksheet}

Names: \underline{\hspace{10cm}}

\begin{enumerate}

  \item Demonstrate your working \mintinline{java}{main} method 
  in the \mintinline{java}{Test} class before you deploy to the server.

  \item Think about how you made your JDBC queries and processed 
  the results.  What would happen if there were no results?  

  \item What values in the database are allowed to be null?  What 
  potential problems does that pose to the end user?
  
  \item What other values in the database could pose a problem 
  with your code?  How (or where) did/should you handle these 
  contingencies?  At the database level?  During a query?  
  In code?  Which solution is ideal?

  \item Demonstrate your working application to a lab instructor 
  and have them sign this worksheet.

\end{enumerate}

Lab Instructor Signature\underline{\hspace{7.5cm}}


\end{document}
